### 2014-11-20 Paper1/paper1B.tex

\subsection*{Dynamic simulation of arm and intended trajectories}
While the derivation above is general, testing its application to human reaching requires choosing plant and actuator models, which themselves require physical parameters. Appropriate plant modeling is well-understood: measured arm segment lengths and self-reported body mass are converted into the plant's inertial, centripetal, and Coriolis terms. Anatomical landmarks and values from Dempster \cite{dempster1955space} and Winter \cite{winter2009biomechanics} relate body mass to limb mass, limb length to limb center of mass, and limb mass and length to moment of inertia. For the actuator, we choose the model and parameters of Burdet et al. \cite{burdet2006stability}. Impedance magnitude is known to be task-dependent \cite{gomi1998task}. We fit a subject-specific constant scale factor relative to the impedance model of Burdet et al. \cite{burdet2006stability} using linear regression, as in Fraon the task-perpendicular data from the first 150 ms of movement in their noise-disturbed trials.

This IS the linear regression from Franklin and Milner 2003. It's jut that we're using task-perpendicular since that's the only part we really care about and so we have to use a constant scale instead of a whole matrix because the subject is unambiguously in motion.

@@

\subsection*{Statistical Analysis}
To determine when the intended trajectory's deviation exceeded the deviation that could be explained by undisturbed reaching, we compared the maximum deviation of the undisturbed reaches to the instantaneous deviation of the pulse-disturbed reaches at 5 ms intervals. The MATLAB statistics toolbox package \cite{MATLAB:2008} was used to perform ANOVA with Tukey-Kramer post-\textit{hoc} test for group differences. We used an alpha level of 0.05 for declaring statistical significance.

>>>>

\subsection*{Dynamic simulation of arm and intended trajectories}
While the derivation above is general, testing its application to human reaching requires choosing plant and actuator models, which themselves require physical parameters. Appropriate plant modeling is well-understood: measured arm segment lengths and self-reported body mass are converted into the plant's inertial, centripetal, and Coriolis terms. Anatomical landmarks and values from Dempster \cite{dempster1955space} and Winter \cite{winter2009biomechanics} relate body mass to limb mass, limb length to limb center of mass, and limb mass and length to moment of inertia. For the actuator, we choose the model and parameters of Burdet et al. \cite{burdet2006stability}. We use a subject-specific constant scale factor, $c$, relative to the model of Burdet et al. \cite{burdet2006stability} to account for task-dependence of the subjects' impedance\cite{gomi1998task}.
\begin{equation}
\tau_{tp}=c(K_p\Delta q+K_d \Delta \dot{q})
\end{equation}
This uses linear regression, as in Franklin et al.\cite{franklin2003adaptation}, except that the task-perpendicular data from the first 150 ms of movement in their noise-disturbed trials is used in place of a stationary task.

@@

\subsection*{Statistical Analysis}
To determine when the intended trajectory's deviation exceeded the deviation that could be explained by undisturbed reaching, we compared the maximum deviation of the undisturbed reaches to the instantaneous deviation of the pulse-disturbed reaches during 100 ms intervals. The MATLAB statistics toolbox package \cite{MATLAB:2008} was used to perform one-tailed T-tests with an alpha level of 0.05. This also provided a confidence interval on the difference.
